---
title: "VAST Beta Settings comparison"
author: "Kelly Mistry"
date: "3/16/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(dplyr)
library(tidyr)
library(R.utils)
library(reshape2)
library(ggplot2)
library(RColorBrewer)
```

## Comparing VAST results with different beta settings with POP data

Options for beta settings that I tried:

-   both betas = 4 (AR1 process for both encounter probability & positive catch temporal coefficients)

-   both betas = 2 (random walk process for both encounter probability & positive catch temporal coefficients)

-   beta 1 = 2, beta 2 = 1 (encounter probability has random walk process, positive catch as fixed intercept temporal coefficients)

```{r data_importing}

# Importing functions from VAST and RE model projects 
source("/Users/kellymistry/Desktop/Raw Data/NOAA/RE_model_v2/scripts/functions.R")
source("/Users/kellymistry/Desktop/Raw Data/NOAA/groundfish_VAST/scripts/01_functions.R")

## Setting up species, year and subregion objects
# species
stock_names <- c("Pacific Ocean Perch" = "Sebastes alutus",
                 "Northern Rockfish" = "Sebastes polyspinis")
#   "Atka Mackerel" = "Pleurogrammus monopterygius")
my_stock_ids <- c("30060",
                  "30420")
#"21921")
names(my_stock_ids) <- stock_names
stock_folder_names <- sub(" ", "_", stock_names)

# Species-specific start and end years
start_years <- c(1990, 
                 1984) 
# 1984)
names(start_years) = stock_names
end_years <- c(2019,
               2019)
# 2019)
names(end_years) = stock_names

# subregions
subregion <- c("WESTERN", "CENTRAL", "EASTERN")

# Number of stocks and subregions
N_stock <- length(stock_names)
N_sub <- length(subregion)

## Import original data sets
# Data set with summarized estimates for each subregion in each year (used with RE model)
GOA_indices_data <- read.csv("/Users/kellymistry/Desktop/Raw Data/NOAA/RE_model_v2/data/BIOMASS_AREA_DATA_TABLE.csv")
# Raw data (used in VAST model), with all of the hauls in each year
GOA_haul_data <- read.csv("/Users/kellymistry/Desktop/Raw Data/NOAA/groundfish_VAST/data/haul.csv")
GOA_CPUE_data <- read.csv("/Users/kellymistry/Desktop/Raw Data/NOAA/groundfish_VAST/data/CPUE.csv")
# Filtering raw data by species and years
GOA_raw_data_list <- list()
for (stock in 1:N_stock) {
  GOA_raw_data_list[[stock]] <- filter_create_VAST_input(GOA_CPUE_data, 
                                                         my_stock_ids, 
                                                         stock_names[stock],
                                                         start_years[stock],
                                                         GOA_haul_data)
  # Checking for NAs in the AreaSwept_km2 column (variable necessary for
  # calculating CPUE, so NA values will cause code to fail)
  if(sum(is.na(GOA_raw_data_list[[stock]][, "AreaSwept_km2"])) > 0) {
    deleted_rows <- which(is.na(GOA_raw_data_list[[stock]][, "AreaSwept_km2"]) == TRUE)
    if (length(deleted_rows) < 10 && length(deleted_rows) > 0) {
      GOA_raw_data_list[[stock]] <- GOA_raw_data_list[[stock]][-c(deleted_rows),]
    } else if (length(deleted_rows) > 10) {
      stop("More than 10 NAs in AreaSwept_km2 column in Data_Geostat") #it might be important to look at why there might be a lot of NAs before deciding to get rid of the rows
    }
  }
  # Adding a column with the subregion for each haul location
  for (i in 1:nrow(GOA_raw_data_list[[stock]])) {
    if (GOA_raw_data_list[[stock]]$Lon[i] <= -157) {
      GOA_raw_data_list[[stock]]$Subregion[i] <-  subregion[1] 
    } else if (GOA_raw_data_list[[stock]]$Lon[i] > -157 && GOA_raw_data_list[[stock]]$Lon[i] <= -147) {
      GOA_raw_data_list[[stock]]$Subregion[i] <-  subregion[2] 
    } else {
      GOA_raw_data_list[[stock]]$Subregion[i] <- subregion[3]
    }
  }
}
names(GOA_raw_data_list) <- sub(" ", "_", stock_names)


# Creating list of data frames for each subregion for each species (6 total)
separated_stock_data <- list()

for (stock in 1:N_stock) {
  separated_stock_data[[stock]] <- lapply(subregion, function(sub) {
    initial_set_up_fun(GOA_indices_data, 
                       stock_names[stock], 
                       start_years[stock], 
                       sub)
  })
  names(separated_stock_data[[stock]]) <- subregion
}
names(separated_stock_data) <- stock_folder_names

# Recording survey years for each species
survey_years <- list()
for(stock in 1:N_stock) {
  survey_years[[stock]] <- lapply(subregion, function(sub) {
    separated_stock_data[[stock]][[sub]]$YEAR
  })
  names(survey_years[[stock]]) <- subregion
}

names(survey_years) <- stock_folder_names


```

```{r VAST_results}

# Beta setting options
beta_list <- c("beta_2s", "beta_2_1","beta_4s")
N_betas <- length(beta_list)

# Create list to hold beta setting VAST results dataframes for results with no missing years
VAST_results_all <- list()
for (beta in 1:N_betas) { 
  # Importing the Table_for_SS3.csv VAST output, which has the bias-corrected 
  # results, and is the model results that should be used in the below calculations
  Table_SS3_data <- read.csv(paste0("/Users/kellymistry/Desktop/Raw Data/NOAA/groundfish_VAST/results/", 
                                    stock_folder_names[1], "/Gamma/", 
                                    beta_list[beta], "/Plots/Table_for_SS3.csv")) 
  # Change the automatic column name for subregions
  colnames(Table_SS3_data)[3] <- "Subregion"
  # Change automatic numeric values to subregion names
  for(sub in 1:N_sub) {
    Table_SS3_data$Subregion[Table_SS3_data$Subregion == sub] <- subregion[sub]
  }
  # Setting specific order of subregion factor levels (for plotting)
  Table_SS3_data$Subregion <- factor(Table_SS3_data$Subregion, levels = subregion)
  # Deleting rows with NAs (non-survey years)
  Table_SS3_data <- na.omit(Table_SS3_data)
  
  # Saving results dataframe to list
  VAST_results_all[[beta]] <- Table_SS3_data
}
names(VAST_results_all) <- beta_list

# Plotting the 3 versions against each other

plot <- ggplot() +
  geom_point(data = VAST_results_all[[1]], aes(x = Year, y = Estimate_metric_tons), color = "red") +
  geom_line(data = VAST_results_all[[1]], aes(x = Year, y = Estimate_metric_tons), color = "red") +
  geom_point(data = VAST_results_all[[2]], aes(x = Year, y = Estimate_metric_tons), color = "blue") +
  geom_line(data = VAST_results_all[[2]], aes(x = Year, y = Estimate_metric_tons), color = "blue") +
  geom_point(data = VAST_results_all[[3]], aes(x = Year, y = Estimate_metric_tons), color = "black") +
  geom_line(data = VAST_results_all[[3]], aes(x = Year, y = Estimate_metric_tons), color = "black") +
  facet_wrap(vars(Subregion), scales = "free") +
  theme_bw() +
  labs(title = "Excluding years: 1996, 1999, 2005, 2009")

```

```{r all_vs_survey_yrs}

### Compare VAST results with just survey year results vs all years (using dummy data)

input_type <- c("all/catches_sampled", "just_survey", "all/catches_1")

# Create list to hold VAST results dataframes
VAST_results_inputs <- list()
for(stock in 1:1) {
  Stock_results <- list()
  for (i in 1:length(input_type)) { 
  # Importing the Table_for_SS3.csv VAST output, which has the bias-corrected 
  # results, and is the model results that should be used in the below calculations
  Table_SS3_data <- read.csv(paste0("/Users/kellymistry/Desktop/Raw Data/NOAA/groundfish_VAST/results/", 
                                    stock_folder_names[stock], "/Gamma/beta_2_1/", 
                                    input_type[i], "/Plots/Table_for_SS3.csv")) 
  # Change the automatic column name for subregions
  colnames(Table_SS3_data)[3] <- "Subregion"
  # Change automatic numeric values to subregion names
  for(sub in 1:N_sub) {
    Table_SS3_data$Subregion[Table_SS3_data$Subregion == sub] <- subregion[sub]
  }
  # Setting specific order of subregion factor levels (for plotting)
  Table_SS3_data$Subregion <- factor(Table_SS3_data$Subregion, levels = subregion)
  # Deleting rows with NAs (non-survey years)
  Table_SS3_data <- na.omit(Table_SS3_data)
  
  # Saving results dataframe to list
  Stock_results[[i]] <- Table_SS3_data
  }
  names(Stock_results) <- input_type
  VAST_results_inputs[[stock]] <- Stock_results
}
names(VAST_results_inputs) <- stock_folder_names[1]

# Plotting all vs survey year results

ggplot() +
  geom_point(data = VAST_results_inputs$Sebastes_alutus[[1]], aes(x = Year, y = Estimate_metric_tons), color = "red") +
  geom_line(data = VAST_results_inputs$Sebastes_alutus[[1]], aes(x = Year, y = Estimate_metric_tons), color = "red") +
  geom_point(data = VAST_results_inputs$Sebastes_alutus[[2]], aes(x = Year, y = Estimate_metric_tons), color = "blue") +
  geom_line(data = VAST_results_inputs$Sebastes_alutus[[2]], aes(x = Year, y = Estimate_metric_tons), color = "blue") +
  geom_point(data = VAST_results_inputs$Sebastes_alutus[[3]], aes(x = Year, y = Estimate_metric_tons), color = "black") +
  geom_line(data = VAST_results_inputs$Sebastes_alutus[[3]], aes(x = Year, y = Estimate_metric_tons), color = "black") +
  facet_wrap(vars(Subregion), scales = "free")



# Creating list with just survey data and data with dummy years from new VAST results, melted so species and subregions can both be faceted
VAST_comparison <- list("just_survey" = VAST_results_all, "all_years" = VAST_all_yrs)
VAST_comparison$just_survey <- melt(VAST_comparison$just_survey, id.vars = colnames(VAST_comparison$just_survey[[1]]))
colnames(VAST_comparison$just_survey)[8] <- "Species"
VAST_comparison$all_years <- melt(VAST_comparison$all_years, id.vars = colnames(VAST_comparison$all_years[[1]]))
colnames(VAST_comparison$all_years)[8] <- "Species"

# Plotting all vs survey year results
colors <- c("all years" = "red", "just survey years" = "black")

plot <- ggplot() +
  geom_point(data = VAST_comparison$all_years, aes(x = Year, y = Biomass), color = "red") +
  geom_line(data = VAST_comparison$all_years, aes(x = Year, y = Biomass), color = "red") +
  geom_point(data = VAST_comparison$just_survey, aes(x = Year, y = Biomass, color = "just survey years")) +
  geom_line(data = VAST_comparison$just_survey, aes(x = Year, y = Biomass), color = "black") +
  facet_wrap(Species ~ Subregion, scales = "free") +
  scale_color_manual(values = colors)
  
ggsave(filename = "just_survey_vs_dummy_data_new-VAST.png", 
        plot = plot, path = here("Plots/betas_2"))


```
